% ----------------------------------------------------------------------------------------
% SECTION TITLE
% ----------------------------------------------------------------------------------------

\vspace{-0.2cm}
\cvsection{Work Experience}

% ----------------------------------------------------------------------------------------
% SECTION CONTENT
% ----------------------------------------------------------------------------------------

\begin{cventries}

  % ------------------------------------------------
  
   \cventry
  {Data Science Intern}
  {Celebal Tech}
  {Jaipur, India}
  {Feb. 2019 - Present}
  {
    \begin{cvitems}
    \item Developed Face Detection model for auto Attendance in company with 93 percent accuracy as Use-case and Deployed using Azure Machine learning services (utilized DataBricks, Transfer learning, Azure ML services, Azure Blob).
    \item Programmed a Demand, Supply Forecaster and auto Supply-chain dashboard generator (PowerBI) as Supply and Operation Planning Usecase (utilized widget in DataBricks, Multivariate ARIMA, PowerBI, Azure Blob).
    \item Currently Working on Cognitive Automation for Supply Chain as Usecase.
    \end{cvitems}
  }

  \cventry
  {Research Intern, under Sumita Kachhwaha}
  {DBT-BIF, Department of Biotechnology, Govt. of India}
  {University of Rajasthan, Jaipur}
  {July. 2018 - Jan. 2019}
  {
    \begin{cvitems}
    \item {Worked on Spark, AWS services, Galaxy to Annotate, Align and Querying Genomic Databases, features requested by industry in Bio-informatics.}
    \item {Created a spark cluster and web enabled tool for finding unique DNA fragment. project includes  phylogeny tree of life creation. it involves use of graph data structure, MongoDB, Searching, allignments, kmer manipulations and bioinformatics for client-servers }
    % \item {Designed a method for allowing key rotations in a multi-master system with a shared database.}
    \item {Designed Algorithms for Extraction, Preprocessing, Sequencing, Searching of Genomic Database and Networking for phylogeny using Python, shell scripting. Used Machine learning and statistical inference for data analysis, classification and prediction in Genomic database}
    \end{cvitems}
  }


  \cventry
  {Full Stack Developer, under Prof. Abhilasha Dangi}
  {CCT Department, University of Rajasthan}
  {Jaipur, India}
  {Feb. 2017 - May. 2017}
  {
    \begin{cvitems}
    \item Worked on a scalable microservice based web application with an extensive technology stack.
    \item Designed and developed critical backend features while
      ensuring type-safety.
    \item Developed and deployed the complete functionality in institution
    \item Adjudged as one of the best project, while being a freshman.
    \end{cvitems}
  }

  % ------------------------------------------------
\end{cventries}

%%% Local Variables:
%%% mode: xelatex
%%% TeX-master: "../resume_twopage"
%%% End:
